%------------------------
% Resume Template
% Author: Hemant Kadam
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\sloppy
\tolerance=1000

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black,
  citecolor=black,
  breaklinks=true
}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\bfseries\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}: #2 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\vspace{-10pt}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Hemant Kadam}} & Mobile: +91-7738705798 \\
  Email: \href{mailto:hemantkadam112@gmail.com}{\underline{hemantkadam112@gmail.com}} & Virar, Mumbai \\
  \href{https://github.com/hemant-i7}{\underline{GitHub: hemant-i7}} & \href{https://www.linkedin.com/in/hemant-kadam-5a1195194/}{\underline{LinkedIn: hemant-kadam}} \\
  \href{https://blogger.hemantkadam.in}{\underline{Blog: blogger.hemantkadam.in}} & \href{https://hemant.engineer}{\underline{hemant.engineer}} \\
\end{tabular*}
\vspace{-6pt}

%-----------SUMMARY-----------------
\section{Summary}
\small{
Software developer with strong expertise in frontend technologies and working knowledge of backend systems. Experienced in developing high-performance web apps using React.js, Next.js, Tailwind CSS, with backend integration through Node.js, NestJS \& MongoDB. Backend \& DevOps oriented: Docker, APIs, deployment. Currently pursuing Computer Engineering at SLRTCE and Intern at Surfboard Ventures. Creator at \href{https://www.youtube.com/@bloggerhemant}{\underline{@BloggerHemant}} with 10K+ subscribers, creating educational content on frontend, AI, SEO and automation. Recognized in multiple national and international hackathons.
}
\vspace{8pt}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Shree L. R. Tiwari College of Engineering (Mumbai University)}{Mumbai, India}
    {Bachelor of Engineering in Computer Science (CGPA: 8.5)}{Sep 2023 – Jun 2026}
  \resumeSubheading
    {Viva College of Diploma Engineering and Technology}{Mumbai, India}
    {Diploma in Computer Engineering (84\%)}{Aug 2020 – Jun 2023}
\resumeSubHeadingListEnd
\vspace{6pt}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Surfboard Ventures}{Virar, Mumbai}
    {Associate Software Engineer Intern}{Feb 2025 – Present}
    \resumeItemListStart
      \resumeItem{Frontend Development}{Developed and optimized modern user interfaces using Next.js 15 and Tailwind CSS.}
      \resumeItem{Secure Payments}{Integrated payment workflows for in-app certifications using Razorpay.}
      \resumeItem{API Integration}{Worked with NestJS backend services for reliable data flow between modules.}
    \resumeItemListEnd

  \vspace{4pt}

  \resumeSubheading
    {Nano Technology (Freelance)}{Remote}
    {Frontend + Automation Engineer Intern}{June 2024 – Feb 2025}
    \resumeItemListStart
      \resumeItem{Automation Workflows}{Built low-code workflow UIs using n8n and LangChain for business process automation.}
      \resumeItem{Dashboard \& API Integration}{Developed interactive dashboards and connected them with Node.js APIs.}
      \resumeItem{Data Management}{Streamlined analytics through MongoDB and responsive frontend visualizations.}
    \resumeItemListEnd

  \vspace{4pt}

  \resumeSubheading
    {Edba Academy (Contract / Freelance)}{Remote}
    {Frontend \& Digital Marketing Engineer}{July 2023 – Sep 2023}
    \resumeItemListStart
      \resumeItem{Frontend Development}{Built responsive web pages using HTML, CSS, Tailwind CSS, and JavaScript.}
      \resumeItem{Digital Marketing \& SEO}{Improved website SEO performance and implemented marketing-related optimizations.}
      \resumeItem{Web Development Services}{Created dynamic, user-friendly interfaces for academy portals.}
    \resumeItemListEnd

  \vspace{4pt}

  \resumeSubheading
    {N. S. Media}{Vasai, Mumbai}
    {Software Developer Intern}{Aug 2022 – Sep 2022}
    \resumeItemListStart
      \resumeItem{Frontend Design}{Created responsive websites using React.js, CSS3, and integrated REST APIs.}
      \resumeItem{Performance Optimization}{Improved page load speed by 20\%.}
      \resumeItem{SEO Enhancements}{Optimized website SEO for better search engine ranking and visibility.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{6pt}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

  \resumeSubItem{\textbf{Arise – AI-Powered Educational Platform}}{
  \href{https://www.ariseai.app/}{\underline{Live}} \,|\, \href{https://github.com/hemant-i7/Arise}{\underline{GitHub}} \\
  Comprehensive AI learning ecosystem with quiz, presentation, and roadmap modules. \textbf{Tech:} Next.js, TypeScript, Tailwind, Gemini API, ElevenLabs, Node.js.}

  \vspace{4pt}

  \resumeSubItem{\textbf{CuraLink – AI Medical Diagnosis System}}{
  \href{https://curalink-two.vercel.app/}{\underline{Live}} \,|\, \href{https://github.com/hemant-i7/curalink-bot}{\underline{GitHub}} \\
  Built multilingual dashboards and integrated LangChain-powered AI diagnosis. \textbf{Tech:} Next.js, Tailwind, LangChain, MongoDB, NextAuth.}

  \vspace{4pt}

  \resumeSubItem{\textbf{TalentLink – Brand-Influencer Collaboration Platform}}{
  \href{https://talentlink-hk.vercel.app/}{\underline{Live}} \,|\, \href{https://github.com/hemant-i7/talentlink}{\underline{GitHub}} \\
  Streamlines collaboration between brand managers and influencers with campaign management and performance tracking. \textbf{Tech:} Next.js, Tailwind, NLP, Node.js, MongoDB.}

  \vspace{4pt}

  \resumeSubItem{\textbf{OneStop – Training \& Placement Hub}}{
  \href{https://onestopclient.vercel.app/}{\underline{Live}} \,|\, \href{https://github.com/hemant-i7/onestop}{\underline{GitHub}} \\
  Job and placement platform with quizzes, ATS matching, and dynamic APIs. \textbf{Tech:} Next.js, Tailwind CSS, Node.js, MongoDB.}

\resumeSubHeadingListEnd
\vspace{6pt}

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeSubItem{Hackathons}{
  \begin{itemize}[leftmargin=*]
    \item 1st Place – IIT Roorkee 44-hour Hackathon
    \item Winner – TechSurf 2025
    \item 1st Runner-up – Webathon 2025 (National)
    \item 2nd Runner-up – Saboo Siddik College Hackathon (National)
    \item 5th Place – Google Build \& Blog Hackathon, Google Office BKC (National)
    \item Top 5 Finalist – Bit \& Build International Hackathon (International)
    \item Top Performer – Global Digital Health Summit Hackathon, NMACC (International)
    \item Top 5 – Technovation, Amrutvahini College Nashik (National)
  \end{itemize}}
\resumeSubHeadingListEnd
\vspace{6pt}

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Frontend}{React.js, Next.js, TypeScript, Tailwind CSS, ShadCN UI}
  \resumeSubItem{Backend \& Cloud}{Node.js, MongoDB, REST APIs}
  \resumeSubItem{Automation \& AI Tools}{LangChain, n8n, Embeddings}
  \resumeSubItem{CMS}{WordPress, Contentstack}
  \resumeSubItem{Tools}{GitHub, VS Code, Postman, Figma, Notion, Vercel}
  \resumeSubItem{Soft Skills}{Analytical Thinking, Collaboration, Problem Solving, Time Management}
\resumeSubHeadingListEnd
\vspace{6pt}

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeSubItem{Contentstack for Developers + Launch}{\href{https://www.edquest.pro/certificate/techsurf-BCWPFANQ}{\underline{Contentstack}}}
  \resumeSubItem{AWS Academy Graduate – Cloud Foundations}{\href{https://www.credly.com/badges/a20568ae-23f2-40c7-8f01-07e48ce9fbe1}{\underline{AWS Academy}}}
  \resumeSubItem{Postman API Fundamentals Student Expert}{\href{https://badgr.com/public/assertions/HGisimb9S-yWLXU3LmS8eA}{\underline{Postman}}}
  \resumeSubItem{Web Front-End Development}{\href{https://www.edba-academy.com/certificates/edba-FGJSOCZ1}{\underline{Edba Academy}}}
\resumeSubHeadingListEnd
\vspace{6pt}

%-----------EXTRACURRICULAR-----------------
\section{Extracurricular}
\resumeSubHeadingListStart
  \resumeSubItem{Blogging \& SEO}{
  Manage and rank 4+ personal websites; improved SEO and generated 2M+ Google organic traffic in 6 months:
  \begin{itemize}[leftmargin=*]
    \item \href{https://marathibeast.com/}{\underline{\textit{MarathiBeast.com}}}
    \item \href{https://blogger.hemantkadam.in/}{\underline{\textit{Blogger.HemantKadam.in}}}
    \item \href{https://hemant.engineer}{\underline{\textit{hemant.engineer}}}
  \end{itemize}}
  \resumeSubItem{Content Creation}{
  Multiple YouTube channels with 49K+ combined subscribers:
  \begin{itemize}[leftmargin=*]
    \item \href{https://www.youtube.com/@HemanTKadaM}{\underline{\textit{Hemant Kadam (33K)}}}
    \item \href{https://www.youtube.com/@bloggerhemant}{\underline{\textit{Blogger Hemant (10K)}}}
    \item \href{https://www.youtube.com/@techhemant8484}{\underline{\textit{Tech Hemant (6K)}}}
  \end{itemize}}
  \resumeSubItem{Workshops \& Mentoring}{
  Conducted technical workshops at SLRTCE: \textit{How to Do Freelancing}, \textit{AI Agent Automation}.}
\resumeSubHeadingListEnd

\end{document}
